QPLIB: A Library of Quadratic Programming Instances

### 2018-02-08 QPLIB-2.2.tex
move wildcard paragraph down
remove artificial space

Our taxonomy is based on a three-fields code of the form ``\textit{OVC}'', where \textit{O} indicates the type of objective function considered, \textit{V} records the types of variables, and \textit{C} designates the types of constraints imposed on the variables. The fields can be given the following values:
%
\begin{itemize}
 \item objective function: (\textit{L})inear, (\textit{D})iagonal convex (if minimization) or concave (if maximization) quadratic, (\textit{C})onvex (if minimization) or (\textit{C})oncave (if maximization) quadratic,  (\textit{Q})uadratic (all other cases);
 %
 \item variables: (\textit{C})ontinuous only, (\textit{B})inary only, (\textit{M})ixed binary and continuous, (\textit{I})nteger (including binary) only, (\textit{G})eneral (all other cases);
 %
 \item constraints: (\textit{N})one, (\textit{B})ox, (\textit{L})inear, (\textit{D})iagonal convex quadratic, (\textit{C})on\-vex quadratic, nonconvex (\textit{Q})uadratic.
  %Note that (\textit{D}) and (\textit{C}) are intended to mean that either $Q^i$ is positive semidefinite and $c_l^i = -\infty$, or $Q^i$ is negative semidefinite and $c_u^i = \infty$. 
    \textcolor{red}{Note that (positive or negative) definiteness of $Q^i$ is a sufficient, but not in general necessary, condition for convexity. As detailed in \S\ref{subsec:final set}, in our taxonomy we mark the constraints ``$C$'' based on the sufficient condition alone, the rationale of this choice being discussed in \S\ref{ssec:reform}.}
  Quadratic constraints with both finite bounds cannot ever be convex (unless $Q^i = 0$, i.e., they are not ``truly'' quadratic constraints).
\end{itemize}
%
The wildcard ``*'' will be used below to indicate any possible choice, and lists of the form ``\{\textit{X}, \textit{Y}, \textit{Z}\}'' will indicate that the value of the given field can freely attain any of the specified values.

@@

@@

\smallskip
It is important to note that the relationships between the different classes can be somehow blurred because reformulation techniques may allow one to move an instance from one class to another. We already mentioned that $x^2 = x \iff x \in \{0, 1\}$, and in general \textit{*M*}---instances with only binary and continuous variables---can be recast as \textit{*CQ}; here nonconvex quadratic constraints take the place of binary variables. More generally, this is also true for \textit{*G*} as long as $\Mcu = \emptyset$, as bounded general integer variables can be represented by binary ones.
Hence, the nonconvexity due to binary variables can always be expressed by means of (nonconvex) quadratic constraints. The converse is also true: when only binary variables are present, all quadratic constraints can be converted into convex ones \cite{BEP09,BEL13}.

>>>>

Our taxonomy is based on a three-fields code of the form ``\textit{OVC}'', where \textit{O} indicates the type of objective function considered, \textit{V} records the types of variables, and \textit{C} designates the types of constraints imposed on the variables. The fields can be given the following values:
%
\begin{itemize}
 \item objective function: (\textit{L})inear, (\textit{D})iagonal convex (if minimization) or concave (if maximization) quadratic, (\textit{C})onvex (if minimization) or (\textit{C})oncave (if maximization) quadratic,  (\textit{Q})uadratic (all other cases);
 %
 \item variables: (\textit{C})ontinuous only, (\textit{B})inary only, (\textit{M})ixed binary and continuous, (\textit{I})nteger (including binary) only, (\textit{G})eneral (all other cases);
 %
 \item constraints: (\textit{N})one, (\textit{B})ox, (\textit{L})inear, (\textit{D})iagonal convex quadratic, (\textit{C})on\-vex quadratic, nonconvex (\textit{Q})uadratic.
  %Note that (\textit{D}) and (\textit{C}) are intended to mean that either $Q^i$ is positive semidefinite and $c_l^i = -\infty$, or $Q^i$ is negative semidefinite and $c_u^i = \infty$. 
    \textcolor{red}{Note that (positive or negative) definiteness of $Q^i$ is a sufficient, but not in general necessary, condition for convexity. As detailed in \S\ref{subsec:final set}, in our taxonomy we mark the constraints ``$C$'' based on the sufficient condition alone, the rationale of this choice being discussed in \S\ref{ssec:reform}.}
  Quadratic constraints with both finite bounds cannot ever be convex (unless $Q^i = 0$, i.e., they are not ``truly'' quadratic constraints).
\end{itemize}

@@

The wildcard ``*'' will be used below to indicate any possible choice, and lists of the form ``\{\textit{X}, \textit{Y}, \textit{Z}\}'' will indicate that the value of the given field can freely attain any of the specified values.

@@

%\smallskip
It is important to note that the relationships between the different classes can be somehow blurred because reformulation techniques may allow one to move an instance from one class to another. We already mentioned that $x^2 = x \iff x \in \{0, 1\}$, and in general \textit{*M*}---instances with only binary and continuous variables---can be recast as \textit{*CQ}; here nonconvex quadratic constraints take the place of binary variables. More generally, this is also true for \textit{*G*} as long as $\Mcu = \emptyset$, as bounded general integer variables can be represented by binary ones.
Hence, the nonconvexity due to binary variables can always be expressed by means of (nonconvex) quadratic constraints. The converse is also true: when only binary variables are present, all quadratic constraints can be converted into convex ones \cite{BEP09,BEL13}.
